EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-04 draft.tex
Update draft.tex

Worker containers include a Python script called \texttt{main.py} running an
infinite loop, continually trying to pull a new population to work on it. Once
\texttt{main.py} receives a message containing configuration data, it creates a
worker object responsible for initializing and running the specified stateless
function (i.e., GA or PSO). Once the function returns a new population, the
worker pushes the results to the \texttt{Output} queue, finishes, and passes
the execution to the main loop. This process is shown in Figure
\ref{fig:worker}.

@@

Figure \ref{fig:experiment_flow} shows the general workflow to run experiments 
in Evo\-Swarm, and three roles users can play. The first step is to develop the 
search strategy algorithms that are going to be used by the multi-population algorithm.

Figure \ref{fig:experiment_flow} shows the general workflow to run experiments
in Evo\-Swarm, and three roles users can play. The first step is to develop the
search strategy algorithms that are going to be used by the multi-population
algorithm; algorithm developers do this. Then administrators are responsible for
the installation and configuration of the application. Once the application is
running, users can start one or several experiments, monitor the execution, and
analyze the results. Depending on the type of experiment executed, users could
have additional needs. As a use case, there are additional scripts for
processing the results of experiments to be used with the COCO framework. In the
next sections, we give more details about these roles and their workflow.

@@

The first step is to develop the search strategy
algorithms that are going to be used by the multi-population algorithm.
Algorithm developers can upload the container definition or images directly to
DockerHub; another option is to upload the container image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub; this
can be defined in DockerHub (or any other registry) too.  Docker Compose
configuration files can reference these containers. When a user needs to deploy
the application, he or she needs to edit the {\tt docker-compose.yml} file
to specify the type and number of containers needed for the application.  The {\tt docker-compose}
application is responsible for starting all the containers, downloading new
versions if it is necessary. After starting the application, users can push
Experiment Definition files and start monitoring the execution in the terminal.
After the experiment is finished, the user must execute another script
that takes as argument the
experiment id to generate a collection of files containing all the
data generated by the experiment in a JSON format.
Researchers can use these files to analyze and plot experiment data.  Python
scripts are included in the repository to plot the running times for the
experiments, and all other plots used in this paper;  there is also a script to
generate the files needed by the COCO framework \cite{hansen2016coco}, which can generate standard
comparisons against other methods.

>>>>

Worker containers include a Python script called \texttt{main.py} running an
infinite loop, continually trying to pull a new population to work on it. Once
\texttt{main.py} receives a message containing configuration data, it creates a
worker object responsible for initializing and running the specified stateless
function (i.e., GA or PSO) with the population and configuration in the message.
Once the function returns the evolved population, the
the main script pushes the results to the \texttt{Output} queue, and continues
the execution to the infinite loop. This process is shown in Figure
\ref{fig:worker}.

@@

Figure \ref{fig:experiment_flow} shows the general workflow to run experiments
in Evo\-Swarm, and the three roles users can play. The first step is to develop the
search strategy algorithms that are going to be used by the multi-population
algorithm; algorithm developers do this. Then administrators are responsible for
the installation and configuration of the application. Once the application is
running, users can start one or several experiments, monitor the execution, and
analyze the results. Depending on the type of experiment executed, users could
have additional needs, in this case there are additional scripts for
processing the results of experiments to be used with the COCO framework. In the
next sections, we give more details about these roles and their workflows.

@@

The first step is to develop the search strategy
algorithms that are going to be used by the multi-population algorithm.
Algorithm developers can upload the container definition or images directly to
DockerHub; another option is to upload the container image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub; this
can be defined in DockerHub (or any other registry) too.  Docker Compose
configuration files can reference these images. When a user needs to deploy
the application, he or she needs to edit the {\tt docker-compose.yml} file
to specify the type and number of containers needed for the application.  The {\tt docker-compose}
application is responsible for starting all the containers, downloading new
versions if it is necessary. After starting the application, users can push
Experiment Definition files and start monitoring the execution in the terminal.
After the experiment is finished, the user must execute another script
that takes as argument the
experiment id to generate a collection of files containing all the
data generated by the experiment in a JSON format.
Researchers can use these files to analyze and plot experiment data.  Python
scripts are included in the repository to plot the running times for the
experiments, and all other plots used in this paper;  there is also a script to
generate the files needed by the COCO framework \cite{hansen2016coco}, which can generate standard
comparisons against other methods.
